---
title: "Schedule Parametrization Sensitivity"
output:
  html_document:
    highlight: textmate
    theme: cerulean
    toc: yes
---

```{r, echo=FALSE}
library(knitr)
```

# Configuration

* Release tag: __MKIIRAC__
* Mode: Experiment
* Environment: Dynamic schedules
* Description: Check different placement and reallocation controlle combinations.
* Goal: Do some combinations perform better than others. 
* GDrive: [Link](https://docs.google.com/spreadsheet/ccc?key=0AnauMDTWhICjdEZtRVZKN2VXMGlyeTl6S184aFg1MHc#gid=6)
* Configuration
  * Initial placement: deactivated
  * Placement: $\{WorstFitDemand, WorstFit, FirstFitDemand\}$
  * Reallocation: $\{KMControl, TControl, None\}$
  * Schedule: $[2000, 3000[$ 
  * Workload: Times MKII - MKII
  * Nodes & VMs & Sizes: Based on infrastructure
  * Executable: `start_benchmark_btree_mkII.py`

## Analysis

For treatment was replicated three times. Mean values are calculated for each treatment. In addition a service quality is calculated. If $r_s$ is the number of successful requests, $r_f$ failed requests, and $r_\hat{f}$ the number of failed requests due to a response time greater than 3 seconds. Service quality is calculated by: 

$$q = \frac{r_s}{r_s+r_f+r_\hat{f}}$$ 

```{r, echo=FALSE, error=FALSE, message=FALSE, prompt=FALSE}
source("analysis - experiments.R")
```

### Summary Table

```{r, results='asis', echo=FALSE}
rownames(result) = seq(nrow(result))
kable(result, row.names=FALSE, digits=2)
``` 

```{r, comment=NA, echo=FALSE}
# Row additions
addtorow = list()
addtorow$pos = as.list(c(-1, seq(0, nrow(result) - 5, by=5), nrow(result)))
addtorow$command = c('\\toprule \n',
                     '\\midrule \n',
                     rep('\\midrule \n', nrow(result) / 5 - 1),
                     '\\bottomrule \n')

# Column names
column.names = c(
  '',
  'Control',
  'Sched',
  '$\\overline{\\text{SD}}$',
  '$\\left \\lceil \\text{SD} \\right \\rceil$',
  '$\\overline{\\text{CPU}}$',
  '$\\overline{\\text{MEM}}$',
  '$\\overline{\\text{RT}}$',
  '$\\left \\lceil \\text{RT} \\right \\rceil$',
  '$\\text{O}$',
  '$\\overline{\\text{MG}}$',
  '$\\text{SQ}$'
  )
names(result) = column.names

# Create table
print(xtable(result, digits=0), 
      sanitize.colnames.function = function(x) {return(x) },
      add.to.row=addtorow,
      include.rownames=FALSE,
      include.colnames=TRUE,
      booktabs=TRUE,
      hline.after=NULL,
      comment=FALSE,
      )
```

```{r, comment=NA, echo=FALSE}
# Create table
print(xtable(result, digits=0), 
      type='html',
      sanitize.colnames.function = function(x) {return(x) },
      include.rownames=FALSE,
      include.colnames=TRUE,
      comment=FALSE,
      )
```

### Dense Summary Table

```{r, results='asis', echo=FALSE}
kable(dense.summary.table, row.names=FALSE, digits=2)
```

```{r, comment=NA,echo=FALSE}
# Define table titles
title = c("Cluster",
          "$\\overline{\\text{SD}}$", "$\\sigma\\text{SD}$", "$\\Delta\\text{SD}$",
          "$\\overline{\\text{MG}}$", "$\\sigma\\text{MG}$", "$\\Delta\\text{MG}$")
names(dense.summary.table) = title


print(xtable(dense.summary.table, digits=2), 
      sanitize.colnames.function = function(x) {return(x)},
      include.rownames=FALSE,
      include.colnames=TRUE,
      booktabs=TRUE,
      comment=FALSE,
      vline.after=c(5),
)   
```


```{r, comment=NA, echo=FALSE}
# Create table
print(xtable(dense.summary.table, digits=2), 
      type='html',
      sanitize.colnames.function = function(x) {return(x) },
      include.rownames=FALSE,
      include.colnames=TRUE,
      comment=FALSE,
      )
```

### MRR Ranking of all controllers

MRR ranking is calculated over metrics: migrations, max, and mean, server demand as already done for simulations: 

```{r, echo=FALSE, prompt=FALSE, warning=FALSE, message=FALSE}
# Build MRR ranking of  experiments
ranking = mrr.ranking(data)

# Load MRR ranking for simulations
source("analysis - simulations.R")

# Combine simulation and experiment MRR rankings
ranking = ddply(ranking, 'CONTROLLER', function(row) {
  # Get simulation ranking for a given controller
  sim = sim_mrr_results[as.character(sim_mrr_results$CONTROLLER) == as.character(row$CONTROLLER),]$rank
  
  # Add simulation ranking to results
  row$ranking.sim = sim
  
  # Add new row that contains experimental and simulation rankings
  return(row)
})
```

```{r, results='asis', echo=FALSE}
kable(ranking, row.names=FALSE, digits=2)
```

```{r, comment=NA,echo=FALSE}
# Define table titles
colnames(ranking) = c('Controller', 'MRR (Exp)', 'MRR (Sim)')

# Create table
print(xtable(ranking, digits=2), 
      sanitize.colnames.function = function(x) {return(x)},
      include.rownames=FALSE,
      include.colnames=TRUE,
      booktabs=TRUE,
      comment=FALSE,
      )
```

```{r, comment=NA, echo=FALSE}
# Create table
print(xtable(ranking, digits=2), 
      type='html',
      sanitize.colnames.function = function(x) {return(x) },
      include.rownames=FALSE,
      include.colnames=TRUE,
      comment=FALSE,
      )
```

